Simulating High-Dimensional Multivariate Data

### 2021-02-25 010-background.Rmd
using renv and box for package management

```{r ch010-background, include=FALSE, cache=FALSE}
devtools::load_all()
library(tidyverse)
d <- 1000
```

@@

```{r ch010-realDataTab}
set.seed(02242021)
num_genes    <- 3
num_patients <- 5
gene_sample  <- sample(example_genes, num_genes)

@@

small_brca %>%
  knitr::kable(booktabs = TRUE, caption = cap)
```

@@

```{r ch010-realDataFig, cache=FALSE, fig.width=8, fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's correlations for three example genes from Table 1. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
GGally::ggpairs(
  data = example_brca[, gene_sample],
  upper = list(continuous = GGally::wrap('cor', method = "spearman"))
) + theme_bw()
```

>>>>

```{r ch010-background, include=FALSE, cache=FALSE}
box::use(
  dplyr[...],
  ggplot2[...],
  stringr[str_sub],
  GGally[ggpairs, wrap],
  knitr[kable]
)
load("data/example_genes.rda")
load("data/example_brca.rda")
d <- 1000
```

@@

```{r ch010-realDataTab}
set.seed(02242021)
num_genes    <- 3
num_patients <- 5
gene_sample  <- sample(example_genes[1:1000], num_genes)

@@

small_brca %>%
  kable(booktabs = TRUE, caption = cap)
```

@@

```{r ch010-realDataFig, cache=FALSE, fig.width=8, fig.cap="Marginal scatterplots, densities, and estimated pairwise Spearman's correlations for three example genes from Table 1. The data possess heavy-right tails, are discrete, and have non-trivial intergene correlations. Modeling these data motivate our simulation methodology."}
ggpairs(
  data = example_brca[, gene_sample],
  upper = list(continuous = wrap('cor', method = "spearman"))
) + theme_bw()
```

### 2021-02-25 030-bigsimr-package.Rmd
using renv and box for package management

@@

```{r ch030-basic-example-setup, echo=TRUE, cache=FALSE}
library(tidyverse)
library(patchwork)
library(bigsimr)

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup()
dist <- distributions_setup()
```

@@

# Step 2. Check admissibility
is_valid_correlation <- function(rho) {
  all(diag(rho) == 1) && matrixcalc::is.positive.semi.definite(rho)
}
is_valid_correlation(R_X)
```

>>>>

```{r ch030-basic-example-setup, echo=TRUE, cache=FALSE}
box::use(
  patchwork[...],
  dplyr[...],
  ggplot2[...],
  tidyr[drop_na],
  bigsimr[bigsimr_setup, distributions_setup],
  JuliaCall[julia_call]
)

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup(pkg_check = FALSE)
dist <- distributions_setup()
```

@@

@@

# Step 2. Check admissibility
julia_call("Bigsimr.iscorrelation", R_X)
```

### 2021-02-25 040-monte-carlo-evaluation.Rmd
using renv and box for package management

```{r ch040-LoadLib040, include=FALSE}
devtools::load_all()
library(tidyverse)
library(bigsimr)

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup()
dist <- distributions_setup()

cores <- as.integer(parallel::detectCores() - 1)
set.seed(10162020)
prob <- 3e-04
```

@@

```{r ch040-gpuVScpuFig, echo=F, out.width='80%', fig.align='center', fig.cap="Computation times as d increases. We filter to the top 1, 5, 10, 15, 20, 25\\% expressing genes (in terms of median expression.)"}
knitr::include_graphics("fig/cpu-gpu-times.png")
```

>>>>

```{r ch040-LoadLib040, include=FALSE}
box::use(
    dplyr[...],
    ggplot2[...],
    patchwork[...],
    tidyr[pivot_longer],
    bigsimr[bigsimr_setup, distributions_setup],
    knitr[include_graphics]
)
load("data/bivariate_normal_sims.rda")
load("data/bivariate_gamma_sims.rda")
load("data/bivariate_nbinom_sims.rda")

load("data/benchmark_dependences.rda")

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup(pkg_check = FALSE)
dist <- distributions_setup()
set.seed(10162020)
prob <- 3e-04
```

@@

```{r ch040-gpuVScpuFig, echo=FALSE, out.width='80%', fig.asp=1, fig.cap="Computation times as d increases."}
dat_long <- benchmark_dependences %>%
  select(-total_time, -n_sim, -needed_near_pd) %>%
  pivot_longer(cols = c(corr_time:sim_time), names_to = "Step", values_to = "Time") %>%
  mutate(dim_size = if_else(dim <= 1000, "Low Dimensional", "High Dimensional"),
         dim_size = factor(dim_size, levels = c("Low Dimensional", "High Dimensional")),
         dim = factor(dim),
         Step = factor(Step,
                       levels = c("corr_time",
                                  "adj_time",
                                  "admiss_time",
                                  "sim_time"),
                       labels = c("Compute Correlation",
                                  "Adjust Correlation",
                                  "Check Admissibility",
                                  "Simulate Data"))) %>%
  rename(Correlation = corr_type, Dimensions = dim)

ggplot(dat_long, aes(Correlation, Time, fill=Step)) +
  geom_bar(position = "stack", stat = "identity") +
  labs(y = "Time (Seconds)") +
  facet_grid(dim_size ~ Dimensions, scales = "free") +
  theme(axis.text.x = element_text(angle = -90))
```

### 2021-02-25 050-examples.Rmd
using renv and box for package management

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
devtools::load_all()
library(tidyverse)
library(bigsimr)

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup()
dist <- distributions_setup()

cores <- as.integer( parallel::detectCores() - 1 )
set.seed(10142020)
```

@@

```{r ch050-estRhoBRCA, echo=TRUE, cache=FALSE}
# Estimate Spearman's correlation on the count data
type <- 'Spearman'
R_S <- bs$cor(as.matrix(brca1000), bs[[type]])
```

@@

nbinom_mom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  s2 <- s^2
  p <- m/s2
  r <- m^2 / (s2 - m)
  c(size = r, prob = p)
}
```

@@

```{r ch050-estMargins, echo = TRUE, eval = TRUE, cache=F}
nbinom_fit <- apply(brca1000, 2, nbinom_mom)
sizes <- nbinom_fit["size",]
probs <- nbinom_fit["prob",]

nb_margins <- make_nbinom_margins(sizes, probs)
```

Notably, the marginal NB probabilities $\hat{p}_i's$ are small --- ranging in the interval $[`r min(probs)` , `r max(probs)`]$. This gives rise to highly variable counts and, typically, less restriction on potential pairwise correlation pairs. Once the functions are defined/executed to complete marginal estimation, we specify targets and generate the desired random vectors using `rvec`:

Now we check admissibility of specified correlation matrix. We begin with the pairwise, 2D MC estimated bounds. And then follow the `r d`D bounds.

```{r ch050-cor-check, echo=TRUE}
# 1. Mapping step first
R_X <- bs$cor_convert(R_S, bs[[type]], bs$Pearson)

# 2a. Check admissibility
is_valid_correlation <- function(rho) {
  all(diag(rho) == 1) && matrixcalc::is.positive.semi.definite(rho)
}
is_valid_correlation(R_X)

# 2b. compute nearest correlation
if (!is_valid_correlation(R_X)) {
  R_Xtilde <- bs$cor_nearPD(R_X)
  ## Quantify the error
  targets <- R_X[lower.tri(R_X)]
  approximates <- R_Xtilde[lower.tri(R_Xtilde)]
  ## R_Xtilde[1:5, 1:5]
  ## norm( x = R_X - R_Xtilde, type = "F" )
  R_X  <- R_Xtilde
}
summary(targets - approximates)
```

While the exact $d \times d$ Spearman correlation matrix is not strictly admissible in our scheme (seen by the non-PSD result above), the approximation is of sufficient quality for most applications with a maximum pairwise of `r max( targets - approximates)` and average error of `r mean( targets - approximates)`.

@@

```{r ch050-runBRCA, echo=FALSE, results=FALSE, cache=FALSE}
dir.create("results", showWarnings = FALSE, recursive = TRUE)
brcaSimRDS <- paste0("results/brca", d, "sim.rds")
if(!file.exists(brcaSimRDS)) {
  set.seed(44)
  n <- 10000
  sim_nbinom <- bs$rvec(n, R_X, nb_margins) 
  colnames(sim_nbinom) <- colnames(brca1000)
  saveRDS(sim_nbinom, brcaSimRDS)
}
sim_nbinom <- readRDS(brcaSimRDS)
```

@@

```{r ch050-makeSimDataFig, cache=FALSE}
if(!file.exists("fig/ch050-simDataFig.png")) {
  p <- GGally::ggpairs(
    data = as.data.frame(sim_nbinom[,example_genes[1:3]]),
    upper = list(continuous = GGally::wrap('cor', method = "spearman"))
  ) + theme_bw()
  ggsave("fig/ch050-simDataFig.png", plot = p, dpi = 300) 
}
```

```{r ch050-simDataFig, fig.cap='Simulated data for three selected high-expressing genes generally replicates the estimated data structure. The data do not exhibit outlying points, but do possess the desired Spearman correlations, central tendencies, and discrete values.'}
knitr::include_graphics('fig/ch050-simDataFig.png')
```

@@

```{r ch050-makeFigBRCA, cache=FALSE}
if(!file.exists("fig/ch050-figBRCA.png")) {
    ## estimate rho from sims and plot
    R_S_hat <- bs$cor(as.matrix(sim_nbinom), bs[[type]])
    ## triplot
    ## png("fig/ch050-figBRCA.png", width = 4, res = 100, units = 'in')
    png("fig/ch050-figBRCA.png", res = 300, width = 5, height = 4, units = 'in')
    par(mfrow=c(1,3))
    plot(R_S[lower.tri(R_S)], R_S_hat[lower.tri(R_S_hat)],
         xlim = c(-1, 1), ylim = c(-1, 1),
         pch = 1, cex = 1, col = rgb(0, 0, 0, 0.05),
         xlab = "Target Correlation", ylab = "Estimated Correlation")
         ## main = "Spearman Cor. Matching")
    abline(a = 0, b = 1, col="red", lty="dashed")
    ## estimate prob,size from sims and plot
    nbinom_size_prob_hat <- apply(sim_nbinom, 2, nbinom_mom)
    plot(sizes, nbinom_size_prob_hat[1,],
         pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
         xlab = "Target Size", ylab = "Estimated Size")
         ## main = "Marginal NB Size Matching")
    abline(a=0, b=1, col="red", lty="dashed")
    plot(log(probs), log(nbinom_size_prob_hat[2,]),
         pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
         xlab = "Target Log Probability", ylab = "Estimated Log Probability")
         ## main = "Marginal NB Prob Matching")
    abline(a=0, b=1, col="red", lty="dashed")
    dev.off()
    par(mfrow=c(1,1))
}
```

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
knitr::include_graphics('fig/ch050-figBRCA.png')
```

@@

```{r ch050-densityEvaluation, include=FALSE, cache=FALSE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep(1, d)
pHat <- mean(apply(sim_nbinom, 1, function(X, y0 = threshold) {
  all(X >= y0)
}))
```

@@

```{r ch050-densityEvaluationECHO, echo=TRUE, cache=FALSE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep(1, d)
mean(apply(sim_nbinom, 1, function(X, y0 = threshold) {
  all( X >= y0)
}))
```

@@

In this small example, we simulate $m=`r m`$ data sets with the number of simulated vectors matching the number of patients in the BRCA data set, $N=`r nrow(brca)`$. Since our simulation is much faster for the Pearson correlation type (see Figure \@ref(fig:ch040-gpuVScpuFig)), we only convert the Spearman correlation matrix once (and ensure its PSD). At each iteration, we estimate the quadratic loss from the specified ${\bf R}_{Spearman}$, producing a distribution of loss values.

```{r ch050-quadlossECHO, echo=TRUE, eval=FALSE, cache=FALSE}
## Simulate random vectors equal to the sample size
N <- nrow(brca)
## create m random vectors and estimate correlation
simRho <- replicate(n = m, expr = {
  tmpSim <- bs$rvec(N , R_X, nb_margins)
  bs$cor(tmpSim, bs[[type]])
}, simplify = FALSE)
## find quadratic loss at each rep
quadLoss <- sapply(simRho, rags2ridges::loss, T = R_S, type = "quadratic")
```

```{r ch050-lossResults, cache=FALSE}
frobeniusRDS <- paste0("results/brca", d, "_frobenius.rds")
if (!file.exists(frobeniusRDS)) {
    N <- nrow(brca1000)
    ## create m random vectors and estimate correlation
    simRho <- replicate(n = m, expr = {
        tmpSim <- bs$rvec(N , R_X, nb_margins)
        bs$cor(tmpSim, bs[[type]])
    }, simplify = FALSE)
    frobenius <- sapply(simRho, rags2ridges::loss, T = R_S, type = "frobenius")
    saveRDS(frobenius, frobeniusRDS)
}
frobenius <- readRDS(frobeniusRDS)
```

@@

```{r ch050-loss-summary, echo=TRUE, eval=TRUE, cache=FALSE}
summary(frobenius)
```

>>>>

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
box::use(
  dplyr[...],
  ggplot2[...],
  patchwork[...],
  bigsimr[...],
  knitr[include_graphics]
)
load("data/example_brca.rda")
load("data/example_genes.rda")

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup(pkg_check = FALSE)
dist <- distributions_setup()

set.seed(10142020)
```

@@

```{r ch050-estRhoBRCA, echo=TRUE, cache=FALSE}
# Estimate Spearman's correlation on the count data
R_S <- bs$cor(as.matrix(brca1000), bs$Spearman)
```

@@

nbinom_mom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  s2 <- s^2
  c(size = m^2 / (s2 - m), prob = m/s2)
}
```

@@

```{r ch050-estMargins, echo = TRUE, eval = TRUE, cache=F}
nbinom_fit <- apply(brca1000, 2, nbinom_mom)
sizes <- nbinom_fit["size",]
probs <- nbinom_fit["prob",]
nb_margins <- make_nbinom_margins(sizes, probs)
```

Notably, the marginal NB probabilities $\hat{p}_i's$ are small --- ranging in the interval $[`r min(probs)` , `r max(probs)`]$. This gives rise to highly variable counts and, typically, less restriction on potential pairwise correlation pairs. Once the functions are defined/executed to complete marginal estimation, we specify targets and generate the desired random vectors using `rvec`. Now we check admissibility of specified correlation matrix. We begin with the pairwise, 2D MC estimated bounds. And then follow the `r d`-D bounds.

```{r ch050-cor-check, echo=TRUE}
# 1. Mapping step first
R_X <- bs$cor_convert(R_S, bs$Spearman, bs$Pearson)

# 2a. Check admissibility
(is_valid_corr <- JuliaCall::julia_call("Bigsimr.iscorrelation", R_X))

# 2b. compute nearest correlation
if (!is_valid_corr) {
  R_X_pd <- bs$cor_nearPD(R_X)
  ## Quantify the error
  targets      <- R_X[lower.tri(R_X, diag = FALSE)]
  approximates <- R_X_pd[lower.tri(R_X_pd, diag = FALSE)]
  R_X  <- R_X_pd
}
summary(abs(targets - approximates))
```

While the exact $d \times d$ Spearman correlation matrix is not strictly admissible in our scheme (seen by the non-positive definite result above), the approximation is of sufficient quality for most applications with a maximum pairwise of `r max( abs(targets - approximates))` and average absolute error of `r mean(abs(targets - approximates))`.

@@

```{r ch050-runBRCA, echo=FALSE, results=FALSE, cache=FALSE}
dir.create("results", showWarnings = FALSE, recursive = TRUE)
brca_sim_path <- paste0("results/brca_", d, "_sim.rds")
if(!file.exists(brca_sim_path)) {
  set.seed(44)
  sim_nbinom <- bs$rvec(10000, R_X, nb_margins) 
  colnames(sim_nbinom) <- colnames(brca1000)
  saveRDS(sim_nbinom, brca_sim_path)
}
sim_nbinom <- readRDS(brca_sim_path)
```

@@

```{r ch050-simDataFig, cache=FALSE, fig.cap="Simulated data for three selected high-expressing genes generally replicates the estimated data structure. The data do not exhibit outlying points, but do possess the desired Spearman correlations, central tendencies, and discrete values."}
set.seed(02242021)
num_genes    <- 3
gene_sample  <- sample(example_genes[1:1000], num_genes)

GGally::ggpairs(
  data = as.data.frame(sim_nbinom[, gene_sample]),
  upper = list(continuous = GGally::wrap('cor', method = "spearman"))
) + theme_bw()
```

@@

```{r ch050-makeFigBRCA, cache=FALSE}
R_S_hat <- bs$cor(as.matrix(sim_nbinom), bs$Spearman)
sim_nbinom_fit <- apply(sim_nbinom, 2, nbinom_mom)
corr_compare <- tibble(
  `Target Correlation` = R_S[lower.tri(R_S, diag = FALSE)],
  `Estimated Correlation` = R_S_hat[lower.tri(R_S_hat, diag = FALSE)]
)
target_compare <- tibble(
  `Target Size` = sizes,
  `Estimated Size` = sim_nbinom_fit[1,]
)
logprob_compare <- tibble(
  `Target Log Probability` = log(probs),
  `Estimated Log Probability` = log(sim_nbinom_fit[2,])
)

if(!file.exists("fig/ch050-figBRCA.png")) {
  p1 <- ggplot(corr_compare, aes(`Target Correlation`, `Estimated Correlation`)) +
    geom_point(alpha = 0.05) + 
    geom_abline(slope = 1, col = "red", lty = "dashed") +
    theme_bw() + coord_equal()

  p2 <- ggplot(target_compare, aes(`Target Size`, `Estimated Size`)) +
    geom_point(alpha = 0.85) + 
    geom_abline(slope = 1, col = "red", lty = "dashed") +
    theme_bw() + coord_equal()

  p3 <- ggplot(logprob_compare, 
               aes(`Target Log Probability`, `Estimated Log Probability`)) +
    geom_point(alpha = 0.85) + 
    geom_abline(slope = 1, col = "red", lty = "dashed") +
    theme_bw() + coord_equal()

  p <- p1 + p2 + p3

  ggsave(filename = "fig/ch050-figBRCA.png",
         plot = p,
         device = "png",
         width = 8,
         height = 4,
         units = "in")
}
```

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
include_graphics('fig/ch050-figBRCA.png')
```

@@

```{r ch050-densityEvaluation, include=FALSE, cache=FALSE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
y0 <- 1
pHat <- mean(apply(sim_nbinom, 1, function(Y) {
  all(Y >= y0)
}))
```

@@

```{r ch050-densityEvaluationECHO, echo=TRUE, cache=FALSE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
y0 <- 1
mean(apply(sim_nbinom, 1, function(Y) {
  all(Y >= y0)
}))
```

@@

In this small example, we simulate $m=`r m`$ data sets with the number of simulated vectors matching the number of patients in the BRCA data set, $N=`r nrow(example_brca)`$. Since our simulation is much faster for the Pearson correlation type (see Figure \@ref(fig:ch040-gpuVScpuFig)), we only convert the Spearman correlation matrix once (and ensure it is positive definite). At each iteration, we estimate the quadratic loss (residual sum of squared errors) from the specified ${\bf R}_{Spearman}$, producing a distribution of loss values.

```{r ch050-quadlossECHO, echo=TRUE, eval=FALSE, cache=FALSE}
# Simulate random vectors equal to the sample size
N <- nrow(example_brca)
# create m random vectors and estimate correlation
simRho <- replicate(n = m, expr = {
  tmpSim <- bs$rvec(N , R_X, nb_margins)
  bs$cor(tmpSim, bs$Spearman)
}, simplify = FALSE)
# Evaluate the residual sum of squared error
sapply(simRho, function(R) sum((R - R_S)^2))
```

```{r loss_examples, include=FALSE, eval=FALSE}
sapply(simRho, function(R) norm(R - R_S))           # norm of diff
sapply(simRho, function(R) norm(R) - norm(R_S))     # diff of norms
sapply(simRho, function(R) sum((R - R_S)^2))        # RSS
sapply(simRho, function(R) mean((R - R_S)^2))       # MSE
sapply(simRho, function(R) sqrt(mean((R - R_S)^2))) # RMSE
sapply(simRho, function(R) mean(abs(R - R_S)))      # MAE
```

```{r ch050-lossResults, cache=FALSE}
frobenius_path <- paste0("results/brca_", d, "_frobenius.rds")
if (!file.exists(frobenius_path)) {
    N <- nrow(example_brca)
    ## create m random vectors and estimate correlation
    simRho <- replicate(n = m, expr = {
        tmpSim <- bs$rvec(N, R_X, nb_margins)
        bs$cor(tmpSim, bs$Spearman)
    }, simplify = FALSE)
    frobenius <- sapply(simRho, function(R) sum((R - R_S)^2))
    saveRDS(frobenius, frobenius_path)
}
frobenius_loss <- readRDS(frobenius_path)
```

@@

```{r ch050-loss-summary, echo=TRUE, eval=TRUE, cache=FALSE}
summary(frobenius_loss)
```

### 2021-02-25 index.Rmd
using renv and box for package management

```{r indexSetup, include=FALSE, cache=FALSE}
library(tidyverse)

set.seed(09212020)
```

@@

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'rslurm'
), 'packages.bib')
```

@@

<!-- 
Here we propose a scheme that ignores the analytic goal --- and, instead, aims to match the empirically-derived estimated correlation data and marginal characteristics.
-->
Another central issue lies in characterizing dependency between components in the high-dimensional random vector.
The choice of correlation in practice usually relates to the eventual analytic goal and distributional assumptions of the data (e.g., non-normal, discrete, infinite support, etc).
For normal data, the Pearson product-moment correlation describes the dependency perfectly. As we will see, however, simulating arbitrary random vectors that match a target Pearson correlation matrix exactly is computationally intense [@Chen2001; @Xia17]. On the other hand, an analyst might consider use of nonparametric correlation measures to better characterize monotone, non-linear dependency, such as Spearman's $\rho$ and Kendall's $\tau$. Throughout, we focus on matching these nonparametric dependency measures, as our aim lies in modeling non-normal data and these rank-based measures possess invariance properties favorable in our proposed methodology.
We do, however, provide Pearson matching with some caveats.

>>>>

```{r indexSetup, include=FALSE, cache=FALSE}
set.seed(09212020)
```

@@

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

@@

<!-- 
Here we propose a scheme that ignores the analytic goal --- and, instead, aims to match the empirically-derived estimated correlation data and marginal characteristics.
-->

Another central issue lies in characterizing dependency between components in the high-dimensional random vector. The choice of correlation in practice usually relates to the eventual analytic goal and distributional assumptions of the data (e.g., non-normal, discrete, infinite support, etc). For normal data, the Pearson product-moment correlation describes the dependency perfectly. As we will see, however, simulating arbitrary random vectors that match a target Pearson correlation matrix exactly is computationally intense [@Chen2001; @Xia17]. On the other hand, an analyst might consider use of nonparametric correlation measures to better characterize monotone, non-linear dependency, such as Spearman's $\rho$ and Kendall's $\tau$. Throughout, we focus on matching these nonparametric dependency measures, as our aim lies in modeling non-normal data and these rank-based measures possess invariance properties favorable in our proposed methodology.
We do, however, provide Pearson matching with some caveats.
